Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-18 WRITEUP/response.md

If the 2mm continuum flux is synchrotron emission, like the 6cm VLA continuum flux,
then it is probably unrelated to the stellar mass of the quasar host galaxy.

So I don't understand why you use it in sect.4.5, para.4 to fit 
the Bruzual & Charlot stellar templates.

Any comment on the very flat spectrum for the lensing elliptical galaxy ?
Is the 6cm emission mainly synchrotron? 
Is the 2mm emission a mix of synchrotron flux and dust flux ?

# RESPONSE:
While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission. We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm. This would also explain the atypical flat spectrum found for the foreground galaxy.

@@

The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron. Assuming a synchrotron index of alpha = 0.7, we find 0.12 mJy at 2mm for the background source. To account for it, we have updated our SED fitting and the resulting parameters throughout the paper using S = 0.27 mJy at 2mm.

We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the unceratinties, where this uncertainty included in the fit included those from absolute flux calibration. Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.

7) BETTER LABELS FOR FIGURE 6 AND TABLE 3 :

Figure 6 and Table 3 are hard to understand, because
there are no velocity labels on Fig.6, and because the order 
of the channels in the Figure (most redshifted first, most blueshifted last),
is the opposite of the order in Table 3 
(most blueshifted first, most redshifted last).

The easiest way to fix this would be to :

a) Put some velocity labels on Fig. 6, at least the center velocity
of each of the seven channels.

b) Reverse the order of the channels in Table 3
(change to most redshifted first, most blueshifted last), to 
agree with the order in Fig.6.

# RESPONSE
We adopted the suggestions.

8) NEED A TABLE TO SUMMARIZE THE CO RESULTS

There are tables where one can find :

--- the continuum photometry data (Table 1),

--- the model lens parameters (Table 2; please add the mass of the lens to this Table,
even though it is not an independent parameter; otherwise people have to search
for it in the text),

--- the model magnification factors (Table 3; possibly add the derived source offset positions),

--- the fits to the IR continuum SED (Table 4).

But there is no table that gives a quick summary of the 
CO results, --- even though they are a large part of the paper.

I suggest that you add a Table, that as a minimum, might give:

--- the CO(2-1) velocities, linewidths, peak fluxes, line-integrated fluxes,
and spatially integrated fluxes.

--- the CO(3-2) similar parameters (when possible).

--- the L'co luminosities corrected for lensing (RXJ1131 + companion).

--- the M(H2) estimated from the CO luminosity (main source + companion).

The same is true of the derived quantities. 
Possible add another Table summarizing the other derived quantites:

--- R_CO (max) ---From whatever is the best method to estimate it.

--- the M_stellar and SFR ---From the SED fitting.

--- the M_dyn If R = 6 kpc and V = 245 km/s (??)

--- the M_gas / M_dyn ratio

--- the M_gas / M_stars ratio

--- the black hole mass

--- the M_BH / M_bulge ratio.

Otherwise, the reader has to search for all these CO values and other quantities in 
many different parts of the text.

# RESPONSE:
We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.

9. TABLE 1, ERROR BARS :

In Sect.2.1, you say the calibration accuracy at 2mm is 15 per cent;
in Sect.2.3, you say the calibration accuracy at 6cm is 10 per cent.

So in Table 1, the 2mm continuum flux error should include the 
10% measuring error plus the 15% calibration error, which add
as sqrt(sum of squares of percent errors) = 18%.

So S(2mm) = 0.80 +/- 0.14 .

Similarly, the 6cm continuum flux error should be the 3% measuring 
error plus the 10% calibration error (root sum squares) = 10.4%.

So S(6cm) = 0.87 +/- 0.09 .

So you need not quote these fluxes to three decimal places.

Because of these flux errors, you also cannot quote the spectral
index of the foreground galaxy to three decimal places
(Sect. 3.3, last sentence).

# RESPONSE:
It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration. To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.

@@

We have fixed the number of decimals in spectral indices in Sec 3.3.

10. FIGURE 4, CAPTION (VLA MAP) :

Because the lensing galaxy is so strong on the VLA map (Fig.4), one
cannot count the contours on the central source. 
So in the caption, 
it might be good to say how many contours there are up to the peak
(= 22 contours ?), and that this corresponds to a flux of 0.9 mJy/b.

An alternative would be to change the contour step after 3 contours
in the VLA map, so that the higher contours would become visible.

But it is probably easiest to just explain the peak value in 
the figure caption.

# RESPONSE
We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.

11. THE BLR LINES ARE REDSHIFTED, NOT BLUESHIFTED.

Sect.5.3, para.1:
Note that Sluse et al. (2007, their sect.7.2) say the Mg absorption doublet is at 0.654.
Sluse et al (their sect.9, Conclusions) also say the narrow emission lines (the NLR)
are measured to be at 0.654.

So in Sect.5.3,par.1 you should quote them correctly as saying that the first set of lines
is at z = 0.654 (not 0.653).

The 1st set of lines (NLR) is at z = 0.654 (not 0.653).
The 2nd set of lines (BLR) is at z = 0.658 (they are more redshifted).

So this sentence is wrong:

"On the other hand, the second set of lines is blueshifted by 780 km/s,.."

This should read "redshifted", not "blueshifted."

(The 780 km/s is also wrong, 
it should be 700 km/s, see below)

"Using the CO line center redshift as the systemic redshift,
we find that the redshift of the first set is fully consistent
with the "systematic" redshift.

--- Change "systematic" to "systemic".

Sect.5.3, para.3, 2nd sentence from end:

Also wrong, here.

Should be "... our CO observations confirm the redshifted BLR lines."

not "blueshifted".

# RESPONSE:
We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.

12. DROP THE "BLACK HOLE RECOIL" SECTION.

You might consider dropping this section entirely.

---The two redshift systems (NLR and BLR) in this quasar have
been known for a long time. 
So the possibility that the NLR-BLR difference is due to a black hole recoil is not 
a new result of your CO-line data, or of your lens modeling, 
which is the main topic of this paper.

---There are many quasars where the BLR redshifts are measured 
to be slightly different from the NLR redshifts.
Sometimes they are more redshifted, sometimes they are more blueshifted.
It is implausible that they all indicate black hole recoils.

---There is a large literature on the redshift differences between
the NLR and BLR lines 
(see e.g., Gaskell, 2009, New Astronomy Reviews, 53, 140; 
Gaskell & Goosmann 2015; Gaskell, Klimek & Nazarova 2007). 
There has been a lot of numerical modeling to explain these differences.

Many simulations favor an inflow of the BLR gas
into the black hole, at a true space velocity of 1000 km/s.

In the BLR, we are actually observing the matter that is flowing into
the black hole. The dominant component in the BLR linewidths is the
rotation of the accretion disk, but there is also an inflow component,
that causes the redshift difference from the NLR lines.

In the simulations, whether the difference is is a blueshift or a redshift
depends on the orientation to the line of sight and the "moving mirror" effect of
the scattering opacity, as well as the clumpiness, etc.

A redshift could result from the disk being more edge-on to our line-of-sight, so 
that clumps in the disk itself block the far side. In this case, we mainly see
the near side, so we see the redshifted inflow component into the black hole.

In the outer parts of the accretion disk, where the density is lower,
there is also a bi-conical outflow, as observed in BAL quasars.

Your phrase 
"...indicating that the BLR of the AGN is "dynamically" offset..."

is not really true. In many current models of the BLR, the region is 
not dynamically offset at all.

The accretion disk rotates around the black hole, and has exactly the same 
cosmological redshift as the host galaxy.

Besides the dominant rotational component, there is also an inflow component, 
that shifts the peak of the line. 
The BLR lines are optically thin, so they go as density squared, 
so the line peak comes from the inner part of the accretion disk, 
where density is highest, 
and where gas flows into the black hole.

For RXJ1131, the picture is further complicated by 
the gravitational lensing, and by the microlensing:

1) MICROLENSING :

Because the NLR is big (100 pc), it is not affected by microlensing.
Because the BLR is small, it is affected by
microlensing in this quasar (Sluse et al.).

It could also be that the microlensing more strongly magnifies
the redshifted part of the BLR lines, 
biasing the apparent redshift to the red side.

2) BLUE SIDE OF THE LINE ATTENUATED BY ABSORPTION :

Another possiblity is that the BLR shows mainly rotation 
in the accretion disk, and also a biconical outflow region
from the outer parts of the accretion disk, as in the BAL phenomenon.

Because of partial, very broad, absorption of the blueshifted flow against the 
AGN continuum, we see stronger emission from the redshifted flow.

Because the system 2 BLR lines in RXJ1131 are very wide (10000 to 20000 km/s), partial
attenuation of the blue sides of the lines could easily shift the apparent 
BLR line centroids toward the red sides of their profiles.

3) UNLIKELY RECOIL VELOCITY :

If the line-of-sight recoil velocity really were 700 km/s, then 
the true space velocity must be even higher, and certainly greater than 
the escape velocity from the host galaxy.

If it is about 1000 km/s, then the black hole moves 1 pc in 1000 years.

So in one rotation time of the host galaxy, 
or in one orbital time of the companion galaxy, 
or in the duration of the starburst, 
or in the duration of the "wet merger" 
(all of these are ~1E8 years), 
the black hole would have moved quite far away from the center of the host galaxy
(10 to 100 kpc !).

This also makes the recoil story implausible, especially for 
many other catalogued quasars and Seyfert galaxies that have differences
between the peaks of the NLR lines and the BLR lines.

# RESPONSE:
a) We have removed the statement regarding "AGN dynamically offset".

@@

We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scneario is highly unlikely and will gladly make the appropriate changes.

3) Assuming that effects (e.g., inflow, geometric effect, micro-lensing) are accountable for part of the velocity offset, then the velocity offset of ~715 km/s would then be at most an upper limit on the line-of-sight velocity. Then  the true recoil velocity is thus most likely to be << 1000 km/s. Ignoring dynamical friction against stellar background and assuming t_recoil ~ 100 Myr, then the crude BH displacement estimate given in the referee report (~few 10kpc) would be possible (as pointed out to be theoretically possible 
by Bonning+07, Loeb07). However, Loeb07 also pointed out that at low ejection speeds (few hundred km/s), the deceleration of the BH (damped) by the external gravitational potential of the galaxy and by dynamical friction (Chandrasekhar 1943; Apj 97, 255) on the background stars, dark matter, and gas would limit the displacement of the slow-moving BH and tend to bring it back to the center of its host galaxy within a few dynamical times (see also Madau & Quataert 04 for analytic results and Boylan-Kolchin+04 for numerical results). Therefore the displacement given in the referee report is unlikely to hold (see also Guedes+11).

Finally, again, we acknowledge that offsets between BLR and NLR lines are quite common in Seyferts and quasars, but typically not as big of an offset. In this paper, we only discuss possible scenarios and do not assert that any one of mentioned scenario is necessary in RXJ1131.

TWO FURTHER SUGGESTIONS FOR SHORTENING THE PAPER:

b) ---Drop the detailed description of the best-fit procedures
(The Markov chain Monte Carlo paragraph in Sect.4.1, paragraph 3).

c) ---Drop the details of the SED fitting procedure in Sect.4.5, 
(especially in the 2nd half of paragraph 1: 
"We impose a uniform prior"...and all the text that follows.)

Both of these sections are very well-written, but will probably be
completely incomprehensible to many readers (including me).

I suggest that you just say that you did best fits to model the lens distribution
and best fits to the SED. 
Simply give a typical reference to the Markov chain, Monte Carlo method.

# RESPONSE:
The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.

@@

However, description of our MCMC sampling has been retained given that conveying the priors and stating how we ensure convergence is necessary for reproducible results and are crucial information for readers to decide on how trust-worthy our inference are from a statistical viewpoint. Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly and thus the inferred physical parameters.

13. FIX THE CONCLUSIONS

Sect.6, para.2: NUMBERS SLIGHTLY INCONSISTENT:

You derive M_gas = 1.38E10 Msun, 
and also M_dyn = 8E10 Msun.

So the ratio f_gas = M_gas / M_dyn = 16.6 percent, not 19 percent.

(This also has to be corrected in the Abstract, and in Sect.5.1.2, para.1).

Sect.6, para.4: DROP THE BLACK HOLE RECOIL STORY.

"...but the optical BLR lines are blueshifted by 780 km/s."

Also wrong here. The BLR lines are redshifted, not blueshifted :

BLR = 0.658 (Sect.5.3, para.1);

CO = 0.6541, NLR lines = 0.654 (Sect.5.3).

If CO(2-1) were at z = 0.658, its frequency would be 139.046 GHz.
True CO(2-1) is at z = 0.6541, so its frequency is 139.373 GHz.

So the apparent z = 0.658 is 327 MHz lower in frequency than systemic,
which corresponds to a Doppler velocity = 327 x 2.151 km/s/MHz,

or V_doppler = 703 km/s higher in velocity (more redshifted)
than the true CO(2-1) velocity centroid at z = 0.6541.

So the BLR lines should be "redshifted by 700 km/s" (not 780 km/s).

OMIT THE REST OF THIS PARAGRAPH,

starting with "This implies that the AGN is offset from the dynamical
center of its host galaxy." all the way to the end to the paragraph.

This is not true. The AGN could be at the center of the galaxy,
and the Doppler shift could just be a radial component (inflow),
superposed on the very fast rotational velocity of the accretion disk.

# RESPONSE:
We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.

@@

For other comments, please refer to our response to point 11 and 12 (since 
they are repeated here).

14. CHANGE FIG.9, (Left Panel) : DROP THE VELOCITY MOMENT MAP (SAME AS FIG.2)

I found Fig.9 (left) very confusing.

You should drop the velocity moment map (its the same map as in Fig.2, anyway), 
and instead, only plot the little crosses
in the source plane, on a more blown-up RA-Dec scale, so the crosses would be more visible.

The diagram is confusing because the moment map is the final observed result 
in the sky plane, after lensing, 
with lensed positions quite different from the original positions in the source plane.

Furthermore, the moment map has a weighting of velocities 
that is biased by the differential lensing, so that the 
red velocities get higher weighting than the blue velocities.

All of this distorted image in the sky plane gets even further distorted 
by convolution with the quite large 4.4" x 2.0" synthesized beam.

The little crosses, however, are model positions (not observed data, unlike the moment map)
in the source plane (not the sky plane),
before lensing, without any intensity weighting, 
and before any convolution with the instrumental beam.

Because this figure is about the result of the best-fit lens models, and because the 
little crosses are the basis for the model p-v curve in the right panel (and not the 
contours on the moment map), 
it would be better to concentrate on the model results in the source plane,
and drop the confusing moment map in the image plane, and drop the synthesized beam ellipse.

That way, on a blown-up diagram, you would have room to put velocity labels on each of the
little crosses, so they could be more easily related to the p-v diagram in the right panel.

Could another interpretation be that instead of tracing a monotonic p-v diagram,
there are, within the errors, just two little clusters of points in the left panel?
---The upper (red wing) cluster and the lower (blue wing) cluster?
Within the errors, the 3 crosses in the red clump almost agree in position,
and the 4 crosses in the blue clump almost agree in position, as well.

The separation between the centroids of the two clusters of points is 1 arcsec, or 7 kpc.
So if this is a central disk, then within the errors, its radius is only 3.5 kpc, not 
the 6 kpc that you quote in many places in the text.

Why do these two clusters of points in Fig.9 (left) not appear in your
p-v diagram in Fig.9 (right)?
In the right panel, why do all the little crosses seem to be evenly spaced?
Is the right panel based on an additional model of a rotating disk, rather than 
the lens model points in Fig.9 (left)?

# RESPONSE:
Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kienamtic components, as shown atop of the observed map. The reconstructed information displays a clear velocity gradient. Taken together with previous results from literature and the intrinsically symmetric line profile, we proceed the next section with dynamical modeling.

### 2016-11-18 WRITEUP/response.md

or simply:

"CO, Radio, Optical, and IR results on 
the Lensed Host Galaxy of the Quasar RXS J1131-1231".

# RESPONSE:
1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl. lens modeling). Therefore, we think that the title is suitable for the paper.

The literature/archival data of the continuum would not be as meaningful without our CO data, e.g. their emission does not convey information about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.

@@

1c) DROP "DYNAMICAL CENTER":

Fig.3, caption:
"...z = 0.6537, which corresponds to the dynamical center of CO(2-1)."

Change to :

"..which corresponds to zero velocity in the CO(2-1) spectrum (Fig.1)."

@@

--- Or else just explain that the V_0 in your Eq(1) comes out to +28 km/s (relative to z=0.6537)
because of the very coarse sampling of your seven 108 km/s-wide bins.

The true line center (relative to z=0.6537) would be at V_0 = +75 km/s if you had
used the full-resolution spectrum (Fig. 1 or Fig.5), rather than the heavily binned channels.

# RESPONSE:
We have corrected nu_LO --> nu_obs.

We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig. 5) and updated the redshift and replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig. 9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.

@@

Does Fig.5 now show the spatially integrated spectrum ? 
What is the difference between this spectrum and the one in Fig.1?

If it is again a spectrum taken at the maximum-intensity point,
then the units on the vertical axis would again have to be [ mJy/beam ].

In Fig.5,it would be good to show what you think is the contribution from the companion galaxy.

# RESPONSE:
We found a bug in generating the map used for previous line-integrated flux extraction. In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relevant channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig. 1). Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this doesn't change our conclusion.

@@

#RESPONSE
While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels. Thus, the uncertainty is more representative using those obtained from the integrated map.

To demonstrate that our S/N are real regardless of the fainter blue wing, we have independently obtained SNR map to confirm our results, where the peak flux in the red peak is 11.46+/-1.95 Jy/B and the blue peak is 5.13 +/- 1.45 Jy/B. 
I think what was confusing was the reported I_CO(3-2)=35.7+/-21.3Jy km/s, for which I missed a sqrt, and it should have been 35.7+/-6.91 Jy km/s, which has been corrected.

Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission is reasonable.

While the additional figure in I_CO is not significant, we keep this 
to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.

@@

"We detect 2mm continuum with an integrated flux density of 1.2+/-0.2 mJy,
with a peak flux of 0.80+/-0.09 mJy/beam, centered on the lensing galaxy.
In the lowest contour (3-sigma), there is a hint of possible emission
from the lensed arc."

Instead of calling this the "deblending procedure",
which people might confuse with deconvolution, 
I would just call it "subtraction of the foreground galaxy", 
or "flux removal by subtraction", because it is just simple 
subtraction, not anything else.

# RESPONSE
We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.

The peak emission in the residual map is 0.39 +/- 0.08 mJy. While the uncertainty associated with the flux measurement of the background source needs to propagate the errors from subtracting the fitted model flux, the significance of the emission in the residual doesn't not. It simply is Data-Model, which is > 4 sigma than the noise. This together with the co-spatial emission supports that flux contribution from the background source to the total integrated 2mm continuum.

@@

Any comment on the very flat spectrum for the lensing elliptical galaxy ?
Is the 6cm emission mainly synchrotron? 
Is the 2mm emission a mix of synchrotron flux and dust flux ?

# RESPONSE:
While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission. We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm. This would also explain the atypical flat spectrum found for the foreground galaxy.

The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron. Assuming a synchrotron index of alpha = 0.7, we find 0.12 mJy at 2mm for the background source. To account for it, we have updated our SED fitting and the resulting parameters throughout the paper using S = 0.27 mJy at 2mm.

We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the uncertainties, where this uncertainty included in the fit included those from absolute flux calibration. Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.

@@

So S(6cm) = 0.87 +/- 0.09 .

So you need not quote these fluxes to three decimal places.

Because of these flux errors, you also cannot quote the spectral
index of the foreground galaxy to three decimal places
(Sect. 3.3, last sentence).

# RESPONSE:
It is of standard practice to report flux measurements from interferometric observations excluding those from the absolute flux calibration. To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.

@@

Also wrong, here.

Should be "... our CO observations confirm the redshifted BLR lines."

not "blueshifted".

# RESPONSE:
We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.

@@

# RESPONSE:
a) We have removed the statement regarding "AGN dynamically offset".

Our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known previously. We have updated this section, adding additional possible interpretation for the offset (e.g. gas inflows, geometric effects) in the discussion.

We agree that it is unlikely that all objects with offset AGN lines are black hole recoils. Here, we are not asserting that the offset arises due to a recoiling black hole, we only discuss the possibility of such interpretation given the data (showing evidence of large offset between BLR and the systemic redshift as traced by our CO data), the high spin parameter, and theoretical expectation from hierarchical model of galaxy evolution, among other possible scenarios, as listed by the referee.

We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scenario is highly unlikely and will gladly make the appropriate changes.

@@

Could another interpretation be that instead of tracing a monotonic p-v diagram,
there are, within the errors, just two little clusters of points in the left panel?
---The upper (red wing) cluster and the lower (blue wing) cluster?
Within the errors, the 3 crosses in the red clump almost agree in position,
and the 4 crosses in the blue clump almost agree in position, as well.

The separation between the centroids of the two clusters of points is 1 arcsec, or 7 kpc.
So if this is a central disk, then within the errors, its radius is only 3.5 kpc, not 
the 6 kpc that you quote in many places in the text.

Why do these two clusters of points in Fig.9 (left) not appear in your
p-v diagram in Fig.9 (right)?
In the right panel, why do all the little crosses seem to be evenly spaced?
Is the right panel based on an additional model of a rotating disk, rather than 
the lens model points in Fig.9 (left)?

# RESPONSE:
Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kinematic components, as shown atop of the observed map. The reconstructed information displays a clear velocity gradient. Taken together with previous results from literature and the intrinsically symmetric line profile, we proceed the next section with dynamical modeling.

@@

To address the referee's concern, we have added in a few lines in the caption to clarify what is being shown in the left panel.

PV: 
As discussed in Sec 4.1.1, we have detailed the evidence and reasons for which we interpret RXJ1131 as a disk galaxy. Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Sec 4.3).

@@

To address the referee's concern and to improve clarify, we have re-iterate in the beginning of the first paragraph of Sec 4.3 that we interpret RXJ1131 as disk galaxy.

Size:
As explained in para. 3 of sec 4.3, we use the maximum observed velocity (i.e.  corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy to the rotation velocity. Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the line center.

Clumps:
With the evidence and reasons listed in the beginning of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.
